\documentclass{report}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{decorations, decorations.markings} 
\tikzset{corner/.style={
  postaction={decorate},
  decoration={markings,mark=between positions 0 and 1 step 0.2 with {\fill (0,0) circle (2pt);}}
  }
}

\input{preamble}
\input{macros}
\input{letterfonts}

\title{\Huge{CS 3377.0U1}\\Quiz 1}
\author{\huge{Hunter Matthews}}
\date{06/05/23}

\begin{document}

\maketitle
\newpage% or \cleardoublepage
% \pdfbookmark[<level>]{<title>}{<dest>}
% -- Chapter #1, Question #7 --
\qs{}{What is a shell? How does it work with the kernel? With the user?}
\pf{Solution}{A shell is the command interpreter. At a basic level, it acts as an interface between you and the operating system. When you enter a command on the screen, the shell interprets the command and calls the program you want. }
\newpage
% -- Chapter #2, Question #6 --
\qs{}{How would you display a list of utilities that compress files?}
\pf{Solution}{You would use apropos.}
\newpage
% -- Chapter #3, Question #3 --
\qs{}{What happens when you give the following commands if the file named done already exists?\\
\$ cp to\_do done\\
\$ mv to\_do done}
\pf{Solution}{For \textbf{\$ cp to\_do done}, if the file already exists, then the command will overwrite the file.\\
\\For \textbf{\$ mv to\_do done}, if the file already exists, then the command will overwrite the file as well, much like the previous command.}
\newpage
% -- Chapter #3, Question #11 --
\qs{}{Which command can you use to look at the first few lines of a file named status.report? Which command can you use to look at the end of the file?}
\pf{Solution}{You would use \textbf{\$ head status.report} to look at the first few lines of the file and you would use \textbf{\$ tail -f status.report}}
\newpage
\end{document}
